---
title: "Luxottica Event"
author: "Luxottica IT"
date: "January 28, 2019"
output:
  html_document:
    df_print: paged
    
    toc_float: true
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r include=FALSE}
suppressWarnings(library(tidyverse))
suppressWarnings(library(stringr))
suppressWarnings(library(data.table))
library(plyr)
library(XML)
library(crayon)
library(lubridate)
library(rjson)
library(readxl) 
#install.packages("DT")
library(DT)

```



```{r include=FALSE}
# Logo
# Define variable containing url
url <- "https://upload.wikimedia.org/wikipedia/commons/thumb/e/e9/Luxottica.svg/220px-Luxottica.svg.png"

# Logo

workDir <- getwd()
set
filePath = paste0(workDir,"/lux")
fileName <- list.files(path=filePath)
SpamData <- data.frame(NA)
# Only Data to consider
keep<- c("AR","BE","BV","DG","MU","PR","PS","TF","VA","VE")
#Event Timezone
etimezone<- "America/Tijuana"


# Read File 

# names <- c("DRG", "ProviderID", "Name", "Address", "City", "State", "ZIP", "Region", "Discharges", "AverageCharges", "AverageTotalPayments", 
#            "AverageMedicarePayments")
# types = 'ccccccccinnn'
# 
# types = 'cccccccccnnccdcccddccc'
# 
# inpatient <- read_tsv('http://594442.youcanlearnit.net/inpatient.tsv', col_names = names, skip=1, col_types = types)


#-----------------------------------------------------
#-------------------------Submitted Data--------------
#-----------------------------------------------------
ctype = c("text","text","text","text","text","numeric","numeric","text","text","text","text","text","text","text")
user <-  read_excel(path=paste0(filePath,"/","User.xlsx"),col_types = ctype)

# Remove all Deleted User 
user <- user[-(which(user$DEL_IND=="X")),]

# combine user namne with First name and last name 
user$full <- paste0(user$NAME_FIRST," ", user$NAME_LAST)


# sent_by_rep <- ddply(sent_by_rep,.(`Business Partner`),mutate,RNAME=as.character(user[which(user$AGENT_ID_ECC==`Business Partner`),c(15)]))







#-----------------------------------------------------
#-------------------------Submitted Data--------------
#-----------------------------------------------------


ctype =c("text","text","text","text","text","text","text","text","text","numeric","numeric","text","text","date","text","text","guess","date","guess","text","text","text")
sent <- read_excel(path=paste0(filePath,"/","sent.xlsx"),col_types = ctype)

glimpse(sent)
sent$`Time Stamp` <-  ymd_hms(sent$`Time Stamp` , tz = "UTC")
#format(ymd_hms("20190120162205",tz="UTC"),tz="CET")
glimpse(sent)

sent$`ZSFA_CARTS_HEAD-ZAEZET` <- paste( 
  str_pad(hour(sent$`ZSFA_CARTS_HEAD-ZAEZET`), 2, side="left",pad="0"),
  str_pad(minute(sent$`ZSFA_CARTS_HEAD-ZAEZET`), 2, side="left",pad="0"),
  str_pad(second(sent$`ZSFA_CARTS_HEAD-ZAEZET`), 2, side="left",pad="0"), 
                                        sep=":")

#gsub("^([0-9]{1,2})", "0\\1\\2", hour(sent$`ZSFA_CARTS_HEAD-ZAEZET`))

# sent$subTime <- ymd_hms(
#     paste0(str_remove_all(sent$`Date in Format YYYYMMDD`,"-"),
#            str_remove_all(sent$`ZSFA_CARTS_HEAD-ZAEZET`,":"))
# )



sent$subTime <- ymd_hms(
    paste0(str_remove_all(sent$`Date in Format YYYYMMDD`,"-"),
           format(ymd_hms(paste0("2015-09-27", str_remove_all(sent$`ZSFA_CARTS_HEAD-ZAEZET`,":"))), format="%H:%M:%S",tz=etimezone))
)

glimpse(sent)




## Check 

sent <- mutate(sent,keep= ifelse(Dv %in% keep,"Keep","Remove"))
sent <- sent[which(sent$keep=="Keep"),]


#sent[707:708,c(14,17)]

#-----------------------------------------------------
#-------------------------Saved Data--------------
#-----------------------------------------------------



ctype =c("text","text","text","text","text","text","text","text","text","numeric","numeric","text","text","date","text","text","guess","date","guess","text","text","text")

saved <- read_excel(path=paste0(filePath,"/","saved.xlsx"),col_types = ctype)

glimpse(saved)
saved$`Time Stamp` <-  ymd_hms(saved$`Time Stamp` , tz = "UTC")
glimpse(saved)

saved$`ZSFA_CARTS_HEAD-ZAEZET` <- saved$`ZSFA_CARTS_HEAD-ZAEZET` <- paste( 
  str_pad(hour(saved$`ZSFA_CARTS_HEAD-ZAEZET`), 2, side="left",pad="0"),
  str_pad(minute(saved$`ZSFA_CARTS_HEAD-ZAEZET`), 2, side="left",pad="0"),
  str_pad(second(saved$`ZSFA_CARTS_HEAD-ZAEZET`), 2, side="left",pad="0"),
  sep=":")

#gsub("^([0-9]{1,2})", "0\\1\\2", hour(sent$`ZSFA_CARTS_HEAD-ZAEZET`))

saved$saveTime <- print(saved$`Time Stamp`,tz="America/Tijuana")
saved$saveHour <- hour(saved$saveTime)
glimpse(saved)
#sent[229:235,c(14,17)]


#format = "%m/%d/%Y %H:%M"




#sent$`Time Stamp` <- as.POSIXct(as.numeric(x[1:5])*86400, origin="1899-12-30",tz="GMT")

#  sent$`Time Stamp` <- as.POSIXct((sent$`Time Stamp`)*86400, origin = "1900-01-01", tz = "UTC")
```


```{r include=FALSE}
Del_cart <- which(saved$`Deletion Indicator`=="X")
if(!is_empty(Del_cart)){
saved <- saved[-Del_cart,]
}

if(dim(saved)[1] > 0){
saved_by_org <- ddply(saved, "SOrg.", summarise, Count = sum( `Order Quantity`) )
names(saved_by_org ) <-c("Org","Unit")
sprintf("Total Unit Saved : %s in CART",sum(saved_by_org$Unit))
sprintf("Total Unit in Saved %s CART",sum(saved_by_org$Unit))


## saved by date
saved_by_org_date <-  ddply(saved, c("SOrg.","`Chngd On`"), summarise, Count = sum( `Order Quantity`) )
names(saved_by_org_date ) <-c("Org","Date","Unit")



}


glimpse(sent)
summary(sent)
d<- count(sent,  c("Surrogate_key","Material")) %>% .[order(.$freq,decreasing = TRUE),]












# h <- count(sent,  c("SOrg.","`ZSFA_CARTS_HEAD-ZAEZET`")) %>% .[order(.$freq,decreasing = TRUE),]
  
 #d[order(d$freq,decreasing = TRUE),]  sent$subTime
sent$subHour <- hour(sent$subTime)

#   
# 
# count(sent,  c("SOrg.","subHour","Surrogate_key")) %>% .[order(.$freq,decreasing = TRUE),]
  



sent_by_org <- ddply(sent, "SOrg.", summarise, Count = sum( `Order Quantity`) )
names(sent_by_org ) <-c("Org","Unit")
sprintf("Total Unit Ordered %s",sum(sent_by_org$Unit))
#alternate Qty by Org 
aggregate(list("Total Qty" = sent$`Order Quantity` ),by=list( "Org " = sent$SOrg.),sum)

# --- By Date 

sent_by_org_date <- ddply(sent, c("SOrg.","`Date in Format YYYYMMDD`"), summarise, Count = sum( `Order Quantity`) )

names(sent_by_org_date ) <-c("Org","Date","Unit")

# --- By Date





sent_qty_brand <-ddply(sent, "Dv", summarise, 
                 Qty = sum(`Order Quantity` ) )

sent_qty_brand

sent_qty_brand_hr <- ddply(sent, c("Dv","subHour"), summarise, 
                 Qty = sum(`Order Quantity` ) )

sent_qty_brand_hr 

sent_qty_brand_hr2 <- ddply(sent, c("Dv","subHour","`Date in Format YYYYMMDD`"), summarise, 
                 Qty = sum(`Order Quantity` ) )

sent_qty_brand_hr 


ggplot(sent_qty_brand_hr,mapping=aes(x=subHour,y=Qty,fill=Dv)) +
  geom_col()

sent_by_rep <- ddply(sent, c("SOrg.","`Business Partner`"), summarise, Count = sum( `Order Quantity`) )

#Add Name of the Rep as column in here
sent_by_rep <- ddply(sent_by_rep,.(`Business Partner`),mutate,Rep_Name =as.character(user[which(user$AGENT_ID_ECC==`Business Partner`),c(15)]))

#sort Data
sent_by_rep[order(sent_by_rep$Count,decreasing = TRUE),] 


#by Customer 
sent_by_customer<- ddply(sent, c("SOrg.","Customer","`First name`","Dv"), summarise, Count = sum( `Order Quantity`) )

#by Customer
sent_by_customer_only<- ddply(sent, c("Customer"), summarise, Count = sum( `Order Quantity`) )



#---------------Heder  subset(sent,select = c(1:6))
 h2_cart <- select(sent,c("Surrogate_key","SOrg."))  %>% 
   distinct(.) %>%
 count(2)
 
 names(h2_cart)<- c("Sales Org","Cart")
h2_cart


 h2_cart_save <- select(saved,c("Surrogate_key","SOrg."))  %>% 
   distinct(.) %>%
 count(2)
 
 names(h2_cart_save)<- c("Sales Org","Cart")
h2_cart


 h2 <- select(sent,c("Surrogate_key","SOrg.","subHour"))  %>% 
   distinct(.) %>%
 count(c(2,3))
 
 names(h2)<- c("Sales Org","HOUR","Cart")
h2


ggplot(h2,mapping=aes(x=HOUR,y=Cart,fill=`Sales Org`)) +
  geom_col()+
  ggtitle("Cart in Hour by ORG")
# Customer COunt 
length(sent_by_customer_only$Customer)
# Mean of COunt 
mean(sent_by_customer_only$Count, na.rm=TRUE)
# 
# > Avg customer Ordered Units are:  `r mean(sent_by_customer_only$Count, na.rm=TRUE) `  from : `r length(sent_by_customer_only$Customer) ` customers.

```

# Event Date : Jan 28 {.tabset .tabset-fade .tabset-pills}

## Summary



Type | Carts | Units
------------- | -------------| ------------- 
<b>Submitted<b>| `r as.character(sum(h2_cart$Cart)) `  | `r as.character(sum(sent_by_org$Unit)) `
<b>Saved </b> | `r if(dim(saved)[1] > 0){ as.character(sum(h2_cart_save$Cart) ) } `  | `r if(dim(saved)[1] > 0){as.character(sum(saved_by_org$Unit)-850)} `
-------------------------------------- 
<!-- >`r sprintf("Total Unit Submitted %s",sum(sent_by_org$Unit)) ` -->

<!-- >`r sprintf("Total Unit in Saved CART %s",if(dim(saved)[1] > 0){sum(saved_by_org$Unit)}) ` -->

>

```{r echo=FALSE}

datatable(sent_by_org_date,caption="Total Units Sent to SAP by Org / Date", style = 'bootstrap', class = 'table-bordered table-condensed',autoHideNavigation = TRUE,rownames = FALSE,options = list(sDom  = '<"top"><"bottom">')) %>% formatStyle(
  'Unit',
  backgroundColor = styleEqual(c("US80", "CA80"), c('gray', 'yellow'),'yellow'))
```

>

```{r echo=FALSE}
if(dim(saved)[1] > 0){
datatable(saved_by_org_date,caption="Total Unit Saved in OSS by Org / Date", style = 'bootstrap', class = 'table-bordered table-condensed',autoHideNavigation = TRUE,rownames = FALSE,options = list(sDom  = '<"top"><"bottom">')) %>% formatStyle(
  'Unit',
  backgroundColor = styleEqual(c("US80", "CA80"), c('gray', 'orange'),'orange'))
}

```


## Detail {.tabset .tabset-fade .tabset-pills}

```{r include=FALSE}
# print(sent_by_org)
#install.packages("DT")
library(DT)


datatable(sent_by_org,caption="Total Unit by Org", style = 'bootstrap', class = 'table-bordered table-condensed',autoHideNavigation = TRUE,rownames = FALSE,options = list(sDom  = '<"top"><"bottom">')) %>% formatStyle(
  'Unit',
  backgroundColor = styleEqual(c("US80", "CA80"), c('gray', 'yellow'),'yellow'))

if(dim(saved)[1] > 0){
datatable(saved_by_org,caption="Total Unit by Org", style = 'bootstrap', class = 'table-bordered table-condensed',autoHideNavigation = TRUE,rownames = FALSE,options = list(searching = FALSE)) %>% formatStyle(
  'Unit',
  backgroundColor = styleEqual(c(0, 1), c('gray', 'yellow'),'red'))

}

# datatable(sent_by_org,caption="Total Unit by Org", class = 'cell-border stripe', width = 400,autoHideNavigation = TRUE,rownames = FALSE,options = list(sDom  = '<"top"><"bottom">')) %>% formatStyle(
#   'Unit',
#   backgroundColor = styleEqual(c(0, 1), c('gray', 'yellow'),'yellow'))


# filter="top", selection="multiple", escape=FALSE, 
#       options = list(sDom  = '<"top">lrt<"bottom">ip')




```

* Total Submitted Unit By Org

`r datatable(sent_by_org, style = 'bootstrap', class = 'table-bordered table-condensed',autoHideNavigation = TRUE,rownames = FALSE,options = list(sDom  = '<"top"><"bottom">')) %>% formatStyle(
  'Unit',
  backgroundColor = styleEqual(c("US80", "CA80"), c('gray', 'yellow'),'yellow'))
`

*** 

* Total Saved Unit By Org

`r 
if(dim(saved)[1] > 0){
datatable(saved_by_org, style = 'bootstrap', class = 'table-bordered table-condensed',autoHideNavigation = TRUE,rownames = FALSE,options = list(sDom  = '<"top"><"bottom">')) %>% formatStyle(
  'Unit',
  backgroundColor = styleEqual(c(0, 1), c('gray', 'yellow'),'red'))
}
`


## Qty by Brand {.tabset .tabset-fade .tabset-pills}
```{r echo=FALSE}


datatable(sent_qty_brand,caption="Qty by Brand", style = 'bootstrap', class = 'table-bordered table-condensed',autoHideNavigation = TRUE,rownames = FALSE,options = list(searching = FALSE))


```

## QTY / Hr {.tabset .tabset-fade .tabset-pills}

```{r echo=FALSE}
datatable(sent_qty_brand_hr,caption="Qty by Hr", style = 'bootstrap', class = 'table-bordered table-condensed',autoHideNavigation = TRUE,rownames = FALSE,options = list(searching = FALSE))
```


## Qty Processed by Rep {.tabset .tabset-fade .tabset-pills}
```{r echo=FALSE}
# sent_by_rep[order(sent_by_rep$Count,decreasing = TRUE),] 
datatable(sent_by_rep,caption="Qty by Hr", style = 'bootstrap', class = 'table-bordered table-condensed',autoHideNavigation = TRUE,rownames = FALSE)
```

## Data By Customer 

> Only Submitted data 
* 9999999 Indicates New Account or Order Open by Other Agent
 
```{r echo=FALSE}
# datatable(sent_by_customer)

datatable(sent_by_customer,extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  ))
```


## Graph 

* By Date 

```{r echo=FALSE}

ggplot(sent_qty_brand_hr2,mapping=aes(x=subHour,y=Qty)) +
  geom_col(aes(fill=Dv))+ facet_wrap(~`Date in Format YYYYMMDD`) 
  

```

* Brands Type Quantity by Hour

```{r echo=FALSE}

sent_qty_brandType_hr <- mutate(sent_qty_brand_hr,"Dv", TYPEBRAND= ifelse(Dv  %in% c("RB", "RX", "RJ", "OO", "DG", "EA", "HC", "MK", "MU"), "Lux", "In HOuse")) %>%
  ddply( c("TYPEBRAND","subHour"), summarise, 
                 Qty = sum(`Qty` ) )



   # Brand Grouping 
  # ggplot(sent_qty_brandType_hr, mapping=aes(x=subHour,y=Qty,fill=TYPEBRAND)) +
  # geom_col()


# 
ggplot(sent_qty_brand_hr,mapping=aes(x=subHour,y=Qty,fill=Dv)) +
  geom_col()


```





***

# Thank You. 
<center><img src="`r url`"></center>  



